---
title: "blfs-standard"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blfs)
```

If you already have a folder you want to turn into a GitHub repository (repo) that uses Box for large files, start with:

```{r echo=FALSE}
#get output before running
tree_output <- capture.output(fs::dir_tree(new_dir))
tree_output[1] <- "~/new_dir"

```

```{r message=FALSE, warning=FALSE}
  new_repo_blfs(dir = new_dir, size = 0.0001) 
```

-   `dir` is the folder you want to set up.

-   `size` is the minimum size (in MB) that counts as a “large” file. Default is **10 MB**, but here we use a small number so our example files are included.

------------------------------------------------------------------------

### File structure before running `new_repo_blfs()`

```{r echo=FALSE}
cat(tree_output, sep = "\n")
```

------------------------------------------------------------------------

### File structure after running `new_repo_blfs()`

```{r echo=FALSE}
tree_output <- capture.output(fs::dir_tree(new_dir))
tree_output[1] <- "~/new_dir"

cat(tree_output, sep = "\n")
```

**What’s new?**

-   There's a new folder, `box-lfs` which contains:

    -   `.boxtracker` pointer files (these replace the large files in GitHub).

    -   An `upload` folder with the real large files, renamed to **hashes** (unique ID codes) so files with the same name don’t overwrite each other.

    -   A `path-hash.csv` file that links the hash back to the original file name and location.

-   There's a new file, `README.md`, the landing page for the repository which alerts users that Box LFS is being used.

-   One of the tracked files is a `.shp` file with multiple files, this gets stored on Box as a `.zip` since a change to any of these files could affect the `.shp` file.

------------------------------------------------------------------------

### What you’ll see when you run `new_repo_blfs()`

1.  **Warning about large files**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("ℹ the following files will no longer be tracked by git:\n")
    cat("example-files/example-shp.*\n")
    cat("example-files/large-file1.txt\n")
    cat("example-files/large-file2.txt\n")

    ```

    This is **expected** — these files are now tracked by Box, not GitHub.

2.  **Message telling you to upload files to Box (if Box Drive isn't installed)**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please upload files from 'example-repo-abc123/box-lfs/upload' to Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")

    ```

    **Do this next:**

    -   Go to the correct folder in Box for your project.

    -   Inside that project’s folder, create a `box-lfs` folder if it doesn’t exist.

    -   Upload everything from your local `upload` folder into Box.

3.  **Prompt asking for the Box link or file path**

    -   If **Box Drive** is installed you'll see a message prompting you to paste the file path on Box to the folder where you want your large files backed up.

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("what is the Box path to the project folder? ")
    ```

    -   If **Box Drive** isn't installed you'll see a message prompting the Box share link to the folder where the large files are backed up (should be in a box-lfs subfolder).

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("what is the Box link to the folder where the data is now backed up? ")
    ```

------------------------------------------------------------------------

## Cloning a GitHub repository using Box LFS

When you clone a GitHub repo that uses Box LFS, you get the code and .boxtracker pointer files — but not the big files themselves. To download those files and put them in the right place, run:

```{r echo=FALSE}
#get intitial file tree 
tree_output <- capture.output(fs::dir_tree(clone_dir))
tree_output[1] <- "~/clone_dir"

```

```{r message=FALSE, warning=FALSE}
clone_repo_blfs(dir=clone_dir, download=dwd)
```

-   `dir` is the folder with the cloned repository.
-   `download` is the folder with the downloaded `.zip` file.

------------------------------------------------------------------------

### Check if a repo uses Box LFS

You can check by running:

```{r}
check_blfs(clone_dir)
```

If it says `TRUE`, the repo uses Box LFS.

------------------------------------------------------------------------

### File structure before running `clone_repo_blfs()`

```{r echo=FALSE}
cat(tree_output, sep = "\n")
```

------------------------------------------------------------------------

### File structure after running `clone_repo_blfs()`

```{r echo=FALSE}
tree_output <- capture.output(fs::dir_tree(clone_dir))
tree_output[1] <- "~/clone_dir"

cat(tree_output, sep = "\n")
```

------------------------------------------------------------------------

### What you’ll see when you run `clone_repo_blfs()`

1.  **Message telling you where to get the files from Box**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please download files from Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    cat("they will be automatically moved to the correct locations from your downloads folder")

    ```

    **Do this next:**

    -   Go to the provided Box link or Box path.

    -   Download the folder (Box will give it to you as a .zip file).

2.  **Prompt to continue**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("hit any key once files have been downloaded to continue setting up the repo")

    ```

    Press Enter when your download is ready.

3.  **Prompt to confirm the zip file location**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat(paste0("Zip file for downloaded data appears to be: ", file.path("~/Downloads/box-lfs-zip.zip"), "\n"))
    cat("Press enter to use this file or provide a different file path.")

    ```

    If this is correct, press Enter. If not, type the correct file path and press Enter.

**With this, your cloned repo will have the correct large files in the right locations.**

------------------------------------------------------------------------

## Pushing a GitHub repository using Box LFS

**Before** you push changes to a repository that uses Box LFS, you need to:

1.  Check if any **tracked files** have been updated.

2.  See if there are **new large files** that should be tracked.

You can do both with:

```{r message=FALSE, warning=FALSE}
push_repo_blfs(dir=clone_dir, size=0.0001)
```

-   `dir` is your local repository folder.
-   `size` is the minimum file size (in MB) that counts as a “large” file. Default is **10 MB**.
-   Here we use a smaller number so our example files are included.

### What you'll see when you run `push_repo_blfs()`:

1.  **Message telling you to upload files to Box**

    You'll only see this message if there are **new or updated files** that need to be uploaded to Box. If there are no changes, the function will finish without printing anything.

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please upload files from 'example-repo-abc123/box-lfs/upload' to Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    ```

    **Do this next:**

    -   Go to the correct folder in Box for your project.
    -   Inside that project’s folder, go to the `box-lfs` folder.
    -   Upload everything from your **local** `upload` folder into Box.

------------------------------------------------------------------------

## Pulling a GitHub repository using Box LFS

**After** you pull changes from a GitHub repository that uses Box LFS, you need to:

1.  Check if any **tracked files** have been updated on Box.

2.  Check if any local tracked files should be pushed before downloading the updated files.

You can do both with:

```{r message=FALSE, warning=FALSE}
pull_repo_blfs(dir=clone_dir, download=dwd)
```

-   `dir` is your local repository folder.
-   `download` is the folder with the downloaded `.zip` file.

### What you'll see when you run `pull_repo_blfs()`:

1.  **Message telling you to upload files to Box**

    You'll only see this message if there are **new or updated files** that need to be **uploaded** to Box. We run this check to make sure that any local changes to the tracked files are

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please upload files from 'example-repo-abc123/box-lfs/upload' to Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    ```

    **Do this next:**

    -   Go to the correct folder in Box for your project.

    -   Inside that project’s folder, go to the `box-lfs` folder.

    -   Upload everything from your **local** `upload` folder into Box.

2.  **Message telling you where to get the files from Box**

    You'll only see this message if there are **new or updated files** that need to be **downloaded** from Box.

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please download files from Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    cat("they will be automatically moved to the correct locations from your downloads folder")

    ```

    **Do this next:**

    -   Go to the provided Box link or Box path.

    -   Download the folder (Box will give it to you as a .zip file).
