---
title: "Main Box LFS Functions (without Box Drive)"
---

```{r, include = FALSE}
library(blfs)
library(testthat)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css style settings, echo = FALSE}
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 14px;
    border-left: 5px solid;
}

hr {
      border: none; 
      border-top: 1px solid; 
      margin-top: 2em; 
      margin-bottom: 2em; 
    }
    
    /* Add spacing between list items */
li {
  margin-bottom: 0.6em;   /* adjust as needed */
}

/* Extra spacing before new numbered list items */
ol > li {
  margin-top: 0.8em;      /* adjust as needed */
}

```

```{r include=FALSE}
library(git2r)

#setting up clean structure for running examples 
  new_dir <- blfs:::create_test_repo(box_lfs=FALSE, examples = TRUE,
                                     source_dir = system.file("extdata", package = "blfs"))
  clone_dir <- blfs:::create_test_repo(box_lfs=TRUE, examples = FALSE, 
                                       source_dir = system.file("extdata", package = "blfs"))
  dwd_dir <- blfs:::create_test_download(source_dir = system.file("extdata", package = "blfs"))
```

If you **don't** have [Box Drive](https://www.box.com/resources/downloads) installed on your computer, you will need to move files between your local project repository and Box. **Box LFS** will rename files and move them around on your local computer, but you'll need to manually download/upload your tracked files.

**Not sure if you've got Box Drive installed?**

```{r eval=FALSE, include=TRUE}
#remotes::install_github("r-box/boxrdrive")
library(boxrdrive)
dr_box_drive()
```
```{r echo=FALSE}
cat("✔ Box Drive installation found.\n")
cat("✔ Box Drive directory available at 'C:/Users/jsmith/Box'.")
```

Below we'll explore the main `blfs` functions that you will use to maintain versioning and backups of your large files.

------------------------------------------------------------------------

## Start Tracking Large Files

If you already have a folder you want to turn into a GitHub repository (repo) that uses Box for large files, start with:

```{r echo=FALSE}
#get output before running
tree_output <- capture.output(fs::dir_tree(new_dir))
tree_output[1] <- "~/new_dir"

```

```{r message=FALSE, warning=FALSE}
  new_repo_blfs(dir = new_dir, size = 0.0001, boxdrive=FALSE)
```

-   `dir` is the folder you want to set up.

-   `size` is the minimum size (in MB) that counts as a “large” file. Default is **10 MB**, but here we use a small number so our example files are included.

<br>

### What you’ll see when you run `new_repo_blfs()`

1.  **Warning about large files**

    ```{r echo=FALSE}
      #making nicer formatted messages and warnings:  
      cat("ℹ the following files will no longer be tracked by git:\n")
      cat("example-files/example-shp.*\n") 
      cat("example-files/large-file1.txt\n") 
      cat("example-files/large-file2.txt\n")
    ```

    This is **expected** — these files are now tracked by Box, not GitHub.

2.  **Message telling you to upload your files**

    ```{r echo=FALSE}
    cat("ℹ Please upload files from 'repo-be201a99726/box-lfs/upload' to Box here: \n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/repo-be201a99726/box-lfs'")
    ```

    You'll have to manually upload the files to Box.

3.  **Prompt asking for the Box link**

    ```{r echo=FALSE}
      #making nicer formatted messages and warnings:  
      cat("what is the Box path to the project folder?")
    ```

    This will update the `.boxtracker` file so others know where the file is located.

4.  **Message telling you your files are now backed up**

    ```{r echo=FALSE}
      cat("✔ Large files are now backed up in Box.")
    ```

<br>

### File structure before running `new_repo_blfs()`

```{r echo=FALSE}
cat(tree_output, sep = "\n")
```

<br>

### File structure after running `new_repo_blfs()`

```{r echo=FALSE}
tree_output <- capture.output(fs::dir_tree(new_dir))
tree_output[1] <- "~/new_dir"

cat(tree_output, sep = "\n")
```

**What’s new?**

-   There's a new folder, `box-lfs` which contains:

    -   `.boxtracker` pointer files (these replace the large files in GitHub).

    -   An `upload` folder with the real large files, renamed to **hashes** (unique ID codes) so files with the same name don’t overwrite each other.

    -   A `path-hash.csv` file that links the hash back to the original file name and location.

-   There's a new file, `README.md`, the landing page for the repository which alerts users that Box LFS is being used.

-   One of the tracked files is a `.shp` file with multiple files, this gets stored on Box as a `.zip` since a change to any of these files could affect the `.shp` file.

------------------------------------------------------------------------

## Cloning a GitHub repository using Box LFS

When you clone a GitHub repo that uses **Box LFS**, you get the code and `.boxtracker` pointer files — but not the big files themselves. To get the location to download those files from and put them in the right place, run:

```{r echo=FALSE}
#get intitial file tree 
tree_output <- capture.output(fs::dir_tree(clone_dir))
tree_output[1] <- "~/clone_dir"

```

```{r message=FALSE, warning=FALSE}
clone_repo_blfs(dir=clone_dir, download=dwd_dir, boxdrive = FALSE)
```

-   `dir` is the folder with the cloned repository.

-   `download` is the path to the download directory.

<br>

### What you’ll see when you run `clone_repo_blfs()`

1.  **Prompt to download files and continue with function**

    ```{r echo=FALSE}
      #making nicer formatted messages and warnings: 
    cat("ℹ Please download files from Box here:\n")
    cat("https://oregonstate.box.com/s/h9g8q6n8lj3u2bwhaalepb0lc28te4n5
    they will be automatically moved to the correct locations from your downloads folder\n")
    cat("hit any key once files have been downloaded to continue setting up the repo")
    ```

    Go to the link or Box path to download all the files, download the entire `box-lfs` folder to your downloads to a `.zip`.

<br>

### Check if a repo uses Box LFS

You can check by running:

```{r}
check_blfs(clone_dir)
```

If it says `TRUE`, the repo uses **Box LFS**.

<br>

### File structure before running `clone_repo_blfs()`

```{r echo=FALSE}
cat(tree_output, sep = "\n")
```

<br>

### File structure after running `clone_repo_blfs()`

```{r echo=FALSE}
tree_output <- capture.output(fs::dir_tree(clone_dir))
tree_output[1] <- "~/clone_dir"

cat(tree_output, sep = "\n")
```

------------------------------------------------------------------------

## Pushing a GitHub repository using Box LFS

**Before** you push changes to a repository that uses Box LFS, you need to:

1.  Check if any **tracked files** have been updated.

2.  See if there are **new large files** that should be tracked.

You can do both with:

```{r message=FALSE, warning=FALSE}
push_repo_blfs(dir=clone_dir, size=0.0001, boxdrive=FALSE)
```

-   `dir` is your local repository folder.
-   `size` is the minimum file size (in MB) that counts as a “large” file. Default is **10 MB**.
-   Here we use a smaller number so our example files are included.

<br>

### What you'll see when you run `push_repo_blfs()`:

1.  **Message telling you to upload files to Box**

    You'll only see this message if there are **new or updated files** that need to be uploaded to Box.

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please upload files from 'example-repo-abc123/box-lfs/upload' to Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    ```

    **Do this next:**

    -   Go to the correct folder in Box for your project.
    -   Inside that project’s folder, go to the `box-lfs` folder.
    -   Upload everything from your **local** `upload` folder into Box.

2.  **Message telling you files have been synced**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("✔ Large files have been synced with Box.")
    ```

------------------------------------------------------------------------

## Pulling a GitHub repository using Box LFS

**After** you pull changes from a GitHub repository that uses Box LFS, you need to:

1.  Check if any **tracked files** have been updated on Box.

2.  Check if any local tracked files should be pushed before downloading the updated files.

You can do both with:

```{r message = FALSE, warning=FALSE}
pull_repo_blfs(dir=clone_dir, download=dwd_dir, boxdrive=FALSE)
```

-   `dir` is your local repository folder.
-   `download` is the folder with the downloaded `.zip` file.

<br>

### What you'll see when you run `pull_repo_blfs()`:

1.  **Message telling you to upload files to Box**

    You'll only see this message if there are **new or updated files** that need to be **uploaded** to Box. We run this check to make sure that any local changes to the tracked files are

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("i Please download files from Box here:\n")
    cat("https://oregonstate.box.com/s/h9g8q6n8lj3u2bwhaalepb0lc28te4n5\n")
    cat("they will be automatically moved to the correct locations from your downloads folder")
    ```

    **Do this next:**

    -   Go to the correct folder in Box for your project.
    -   Inside that project’s folder, go to the `box-lfs` folder.
    -   Upload everything from your **local** `upload` folder into Box.

2.  **Prompt to get new files from Box**

    You'll only see this message if there are **new or updated files** that need to be **downloaded** from Box.

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("Please download files from Box here:\n")
    cat("'Wildfire_Water_Security/02_Nodes/your node/Projects/example-repo-abc123/box-lfs'\n")
    cat("they will be automatically moved to the correct locations from your downloads folder")

    ```

    **Do this next:**

    -   Go to the provided Box link or Box path.
    -   Download the folder (Box will give it to you as a `.zip` file).
    -   Hit any key in **R** to finish running the function.
    -   Confirm the download folder is correct or specify download path

3.  **Message telling you your large files have been fetched:**

    ```{r echo=FALSE}
     #making nicer formatted messages and warnings: 
    cat("✔ Large files have been fetched from Box and put in repository.\n")
    cat("✔ Large files have been synced with Box.\n")

    ```
    
```{r include=FALSE}

#remove temp
  unlink(new_dir)
  unlink(clone_dir)
  unlink(dwd_dir)

```
